Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2013-01-15 many.tex
Threshold figure converted to B&W, changed x-axis label for pfore.pdf

\begin{figure}
  \includegraphics[width=\columnwidth]{threshold.pdf}
  \caption{\label{fig:threshold-rate-dependence} The mean foreground
    rate uncertainty, Eq.~\eqref{eq:delta-R-definition}, as a function
    of threshold for data sets with $\Lambda_f = 100$ (blue),
    $\Lambda_f = 10$ (green), and $\Lambda_f = 1$ (red).  Recall that
    $\Lambda_f$ is the mean number of foreground events above
    $x_\mathrm{th} = 8$.  The total background rate, $R_b\left(
    x_\mathrm{th} \right)$, is shown in black; we fix $R_b \left(
    x_\mathrm{th} = x_1 = 8\right) = 1$, so on average there is one
    background event above $x = 8$.  For $x_\mathrm{th} \gtrsim x_1$,
    increasing the threshold tends to increase the foreground rate
    uncertainty because the rate is foreground-dominated and fewer
    events are included in the data set.  For $x_\mathrm{th} \lesssim
    x_1$, the background rate dominates at small loudness, and the
    foreground rate uncertainty asymptotes to the counting error on
    the events that stand out from the background, $\Delta R_f / R_f
    \simeq 1/\sqrt{\Lambda_f}$.  Note that this uncertainty applies
    even when the total number of background events is orders of
    magnitude larger than the number of foreground events.  When a
    threshold must be chosen, it is safest---in the sense of producing
    the minimal foreground rate uncertainty---to choose the threshold
    \emph{well into the background-dominated loudness regime}; the
    extra background events in the data set do not affect the estimate
    of the foreground rate, and, when the background distribution is
    parameterized, can help to better determine these parameters (see
    \S~\ref{sec:gw-overlapping-template}). }
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{threshold.pdf}
  \caption{\label{fig:threshold-rate-dependence} The mean foreground
    rate uncertainty, Eq.~\eqref{eq:delta-R-definition}, as a function
    of threshold for data sets with $\Lambda_f = 100$ (solid line),
    $\Lambda_f = 10$ (dashed line), and $\Lambda_f = 1$ (dash-dotted
    line).  Recall that $\Lambda_f$ is the mean number of foreground
    events above $x_\mathrm{th} = 8$.  The total background rate,
    $R_b\left( x_\mathrm{th} \right)$, is shown by the dotted line; we
    fix $R_b \left( x_\mathrm{th} = x_1 = 8\right) = 1$, so on average
    there is one background event above $x = 8$.  For $x_\mathrm{th}
    \gtrsim x_1$, increasing the threshold tends to increase the
    foreground rate uncertainty because the rate is
    foreground-dominated and fewer events are included in the data
    set.  For $x_\mathrm{th} \lesssim x_1$, the background rate
    dominates at small loudness, and the foreground rate uncertainty
    asymptotes to the counting error on the events that stand out from
    the background, $\Delta R_f / R_f \simeq 1/\sqrt{\Lambda_f}$.
    Note that this uncertainty applies even when the total number of
    background events is orders of magnitude larger than the number of
    foreground events.  When a threshold must be chosen, it is
    safest---in the sense of producing the minimal foreground rate
    uncertainty---to choose the threshold \emph{well into the
      background-dominated loudness regime}; the extra background
    events in the data set do not affect the estimate of the
    foreground rate, and, when the background distribution is
    parameterized, can help to better determine these parameters (see
    \S~\ref{sec:gw-overlapping-template}). }
\end{figure}
